---
title: "homework_8_canids"
author: "ZJG"
date: "March 9, 2017"
output: html_document
---

```{r}
file=read.csv('/home/eeb177-student/Desktop/eeb234/eeb-177/classwork/canids/test_3.csv', header = FALSE)
file

```

```{r}
names <- file[ , 'V1'] 
species <- file[, 'V2']
species_names <- paste(names,species)
file[,'names'] <- species_names
newfile <- file[order(file$V4),]
newfile
```
ggplot

```{r}
ggplot(data = newfile, aes(x = V3, y = names)) + geom_segment(aes(xend = V3+V4, yend= names, color = V1), show.legend = FALSE) + labs(title = "Canids Stratographic Ranges", y = "Species Names", x = "Mya") + theme(axis.text.y = element_text(size=2), axis.text.x =element_text(size=12))
       
````

Answers to Questions

Taxonomic group displayed: Canids

How many unique fossil species are contained within it: 

```{r}
species <- unique(newfile["names"])
nrow(species)

```

How many unique fossil genera are there?

```{r}
genera <- unique(newfile["V1"])
nrow(genera)

```

Species with the longest span:
Cormocyon copei

```{r}
cats=read.csv('/home/eeb177-student/Desktop/eeb234/eeb-177/classwork/canids/cats.csv', header = FALSE)
cats

```

```{r}
names <- cats[ , 'V1'] 
species <- cats[, 'V2']
species_names <- paste(names,species)
cats[,'names'] <- species_names
newcats <- cats[order(file$V4),]
newcats
```
ggplot

```{r}
ggplot(data = newcats, aes(x = V3, y = names)) + geom_segment(aes(xend = V3+V4, yend= names, color = V1), show.legend = FALSE) + labs(title = "Canids Stratographic Ranges", y = "Species Names", x = "Mya") + theme(axis.text.y = element_text(size=2), axis.text.x =element_text(size=12))
       
````

Answers to Questions

Taxonomic group displayed: Felidae

How many unique fossil species are contained within it: 

```{r}
species <- unique(newcats["names"])
nrow(species)

```

How many unique fossil genera are there?

```{r}
genera <- unique(newcats["V1"])
nrow(genera)

```
Species with the longest span:

Caracal caracal



# Exploring Data Frames

```{r}
df <- data.frame( first = c('Zack'), last = c('Gold'), lucky_number= c(8), stringsAsFactors = FALSE)
df <- rbind(df, list('Kelcie', 'Chiquillo', 17))
df <- cbind(df, coffeetime = c(TRUE,TRUE))
df
```

Challenge 2
```{r}

source(file = '/home/eeb177-student/scripts/load-gapminder.R')


```

Challenge 3
country and continent are factor type
pop, lifeExp, and gdpPercap are numeric vectors
year is an int vector

#Subsetting

```{r}
x <- c(5.4, 6.2, 7.1, 4.8, 7.5)
names(x) <- c('a', 'b', 'c', 'd', 'e')
print(x)
x[2:4]
x[c('b','c','d')]
x[-c(1,5)]


```

```{r}
x[-which(names(x) == "g")]
```
Challenge 2
empty vector since no number to entry g, no true values therefore returns empty()

Challenge 3
```{r}
xsubset = x[7 > x & x > 4]
```

Challenge 4

```{r}
m <- matrix(1:18, nrow=3, ncol=6)
print(m)
```

```{r}
m[2,c(4,5)] # D
```
Challenge 5
```{r}

xlist <- list(a = "Software Carpentry", b = 1:10, data = head(iris))
xlist$b[2]
```

Challenge 6
mod$df.residual



Challenge 7

1. = should be == to satify boolean
2. rewrite as ,-c(1:4)
3. need to select the column >80,]
4. need c(4,5)
5. %in% c(2002,2007),

Challenge 8

Data frames can not be subsetted on one dimension.

# Publication quality graphs
ggplot(data = gapminder, aes(x = year, y = lifeExp)) + geom_point()

Challenge 2
ggplot(data = gapminder, aes(x = year, y = lifeExp, color = continent)) + geom_point()

Challenge 3
switching the order of the line and point layers changes which of the graphs is plotted on top of the other

Challenge 4
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(size = 1.5, color = 'blue') + scale_x_log10() + geom_smooth(method="lm", size=1.5)

Challenge 4b
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp,color = continent)) +
  geom_point(size = 1.5, pch=17) + scale_x_log10() + geom_smooth(method="lm", size=1.5)


Challenge 5

ggplot(data = gapminder, aes(x = gdpPercap, fill=continent)) +
 geom_density(alpha=0.6) + facet_wrap( ~ year) + scale_x_log10()







       