---
title: "lab_hw_8"
author: "ZJG"
date: "March 1, 2017"
output: html_document
---

```{r}
housing <- read.csv("Rgraphics/dataSets/landdata-states.csv")
head(housing[1:5])
```

```{r}
hist(housing$Home.Value)
```

```{r}
library(ggplot2)
ggplot(housing, aes(x = Home.Value)) +
  geom_histogram()
```

```{r}
plot(Home.Value ~ Date,
     data=subset(housing, State == "MA"))
points(Home.Value ~ Date, col="red",
       data=subset(housing, State == "TX"))
legend(1975, 400000,
       c("MA", "TX"), title="State",
       col=c("black", "red"),
       pch=c(1, 1))
```

```{r}
ggplot(subset(housing, State %in% c("MA", "TX")),
       aes(x=Date,
           y=Home.Value,
           color=State))+
  geom_point()
```


```{r}
hp2001Q1 <- subset(housing, Date == 2001.25) 
ggplot(hp2001Q1,
       aes(y = Structure.Cost, x = Land.Value)) +
  geom_point()
```

```{r}
ggplot(hp2001Q1,
       aes(y = Structure.Cost, x = log(Land.Value))) +
  geom_point()
```



```{r}
hp2001Q1$pred.SC <- predict(lm(Structure.Cost ~ log(Land.Value), data = hp2001Q1))

p1 <- ggplot(hp2001Q1, aes(x = log(Land.Value), y = Structure.Cost))

p1 + geom_point(aes(color = Home.Value)) +
  geom_line(aes(y = pred.SC))
```

```{r}
p1 +
  geom_point(aes(color = Home.Value)) +
  geom_smooth()
```


```{r}
p1 + 
  geom_text(aes(label=State), size = 3)
```

```{r}
#install.packages("ggrepel") 
library("ggrepel")
p1 + 
  geom_point() + 
  geom_text_repel(aes(label=State), size = 3)
```


```{r}
p1 +
  geom_point(aes(color=Home.Value, shape = region))
```


## Exercise 1

```{r}
dat <- read.csv("Rgraphics/dataSets/EconomistData.csv")
head(dat)
```

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point()
```

Create a scatter plot with CPI on the x axis and HDI on the y axis.

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point()
```


Color the points blue.
```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(color="blue")
```

Map the color of the the points to Region.

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region))
```

Make the points bigger by setting size to 2

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2)
```

Map the size of the points to HDI.Rank

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region))

```
```{r}
p2 <- ggplot(housing, aes(x = Home.Value))
p2 + geom_histogram()
```

```{r}
p2 + geom_histogram(stat = "bin", binwidth=4000)
```

```{r}
housing.sum <- aggregate(housing["Home.Value"], housing["State"], FUN=mean)
rbind(head(housing.sum), tail(housing.sum))
```

```{r}
ggplot(housing.sum, aes(x=State, y=Home.Value)) + 
  geom_bar(stat="identity")
```
Exercise II

Re-create a scatter plot with CPI on the x axis and HDI on the y axis (as you did in the previous exercise).

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2)
```

Overlay a smoothing line on top of the scatter plot using geom_smooth.

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2) + geom_smooth()
```
Overlay a smoothing line on top of the scatter plot using geom_smooth, but use a linear model for the predictions. Hint: see ?stat_smooth.

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2) + geom_smooth(method ="lm")
```

Overlay a smoothing line on top of the scatter plot using geom_line. Hint: change the statistical transformation.
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(aes(color= Region),size=2) + geom_line(stat="identity")
```

BONUS: Overlay a smoothing line on top of the scatter plot using the default loess method, but make it less smooth. Hint: see ?loess.

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2) + geom_smooth(span = .2)
```


Scale
```{r}
p3 <- ggplot(housing,
             aes(x = State,
                 y = Home.Price.Index)) + 
        theme(legend.position="top",
              axis.text=element_text(size = 6))
(p4 <- p3 + geom_point(aes(color = Date),
                       alpha = 0.5,
                       size = 1.5,
                       position = position_jitter(width = 0.25, height = 0)))
```

```{r}
p4 + scale_x_discrete(name="State Abbreviation") +
  scale_color_continuous(name="",
                         breaks = c(1976, 1994, 2013),
                         labels = c("'76", "'94", "'13"))
```

```{r}
p4 +
  scale_x_discrete(name="State Abbreviation") +
  scale_color_continuous(name="",
                         breaks = c(1976, 1994, 2013),
                         labels = c("'76", "'94", "'13"),
                         low = "blue", high = "red")
```

```{r}
p4 +
  scale_color_continuous(name="",
                         breaks = c(1976, 1994, 2013),
                         labels = c("'76", "'94", "'13"),
                         low = muted("blue"), high = muted("red"))
```

```{r}
p4 +
  scale_color_gradient2(name="",
                        breaks = c(1976, 1994, 2013),
                        labels = c("'76", "'94", "'13"),
                        low = "blue",
                        high = "red",
                        mid = "gray60",
                        midpoint = 1994)
```

Exercise 3

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2)
```
```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2) + scale_y_continuous("Human Development Index") + scale_x_continuous("Consumer Price Index") + scale_colour_hue(h = c(0, 180), l = 50)
```

```{r}
ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank)) + geom_point(aes(color= Region),size=2) + scale_y_continuous("Human Development Index") + scale_x_continuous("Consumer Price Index") + scale_colour_manual(values= c("darkblue", "blue", "lightblue", "cyan", "darkcyan", "lightcyan"))
```

Faceting
```{r}
p5 <- ggplot(housing, aes(x = Date, y = Home.Value))
p5 + geom_line(aes(color = State))
```

```{r}
(p5 <- p5 + geom_line() +
   facet_wrap(~State, ncol = 10))
```

```{r}
p5 + theme_linedraw()
```

Final Exercise

```{r}
country_labels <- c("Russia", "Venezula", "Iraq", "Myanmar", "Sudan", "Afghanostan", "Congo", "India", "Brazil", "Argentina", "Greece", "Italy", "Spain", "France", "US", "Botswana", "Cape Verde", "Rwanda", "Bhutan", "Barbados", "Japan", "China", "Germany", "Britain", "Singapore", "New Zealand", "Norway", "South Africa")

ggplot(dat, aes(x = CPI, y = HDI, size = HDI.Rank, label = Country) ) + theme_minimal()+  geom_point(shape =21, aes(color= Region,), size=2, fill = "white") + scale_y_continuous("Human Development Index") + scale_x_continuous("Corruption Protections Index") + scale_colour_manual(values = c("darkgreen", "darkslategrey", "aquamarine4", "darkcyan", "firebrick3", "darkred"  )) + geom_smooth(method = "lm", formula = y ~ poly(x,3), se= FALSE , color = "red", size = 0.5) + geom_text_repel(aes(label=Country), size = 3, check_overlap = TRUE, position = position_dodge(.1)) + 
```

